Spatial Analysis

### 2021-07-08 Scripts/spatial_analisis.Rmd
re-plotted for only scop, flounder and bsb

Species <- c(
  "Scomber scombrus",
  "Doryteuthis (Amerigo) pealeii", #longfin squid WE DONT HAVE IT
  "Peprilus triacanthus", # butterfish
  "Illex illecebrosus", #shortfin squid
  "Paralichthys dentatus", #summer flounder
  "Stenotomus chrysops", #Scup"
  "Centropristis striata", # black sea bass
  "Pomatomus saltatrix", # Bluefish
  "Lopholatilus chamaeleonticeps", #golden tilefish
  "Caulolatilus microps", #blueline tilefish
  "Clupea harengus" # Atlantic herring (Jointly in State and Federal Waters)
  )

@@

This map shows the average proportion of the extrapolated value from the whole study period within each State's water.

@@

ggplot(data = subset(data_grid, !is.na(mean))) +
  geom_tile(
    aes(
      x = lon,
      y = lat,
      fill = mean,
      col = mean
    )
  ) +
  geom_sf(data = land_sf, aes()) +
  facet_wrap(~ state  +  region,
             ncol = 4) +
  labs(x = "Longitude", y = "Latitude") +
  scale_fill_viridis("Mean Proportion", alpha = 0.8) +
  scale_color_viridis("Mean Proportion", alpha = 0.8) +
  my_ggtheme_p()
```

@@

### Per species maps

@@

# The plot
land_sf %>% 
  left_join(state_fit,
            by = "state") %>% 
  ggplot() +
  geom_sf(aes(fill = mean_per)) +
  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8) +
  facet_grid(spp ~ label) +
  labs(x = "Longitude", 
       y = "Latitude") +
  my_ggtheme_p(facet_tx_s = 20,
               leg_pos = "bottom",
               axx_tx_ang = 45,
               ax_tx_s = 12,
               ax_tl_s = 18,
               hjust = 1) +
  theme(legend.key.width = unit(4,"line")) +
  ggsave(filename = "proportion_chg_spp.jpg",
         plot = ggplot2::last_plot(),
         path = my_path("R","Figures"),
         width = 14,
         height = 17
         )

@@

>>>>

Species <- c(
  # "Scomber scombrus",
  # "Doryteuthis (Amerigo) pealeii", #longfin squid WE DONT HAVE IT
  # "Peprilus triacanthus", # butterfish
  # "Illex illecebrosus", #shortfin squid
  "Paralichthys dentatus", #summer flounder
  "Stenotomus chrysops", #Scup"
  "Centropristis striata"#, # black sea bass
  # "Pomatomus saltatrix", # Bluefish
  # "Lopholatilus chamaeleonticeps", #golden tilefish
  # "Caulolatilus microps", #blueline tilefish
  # "Clupea harengus" # Atlantic herring (Jointly in State and Federal Waters)
  )

@@

This map shows the aggregated extrapolated value from all three species per State average across the whole study period within each State's water.

@@

ggplot(data = subset(data_grid, !is.na(mean))) +
  geom_tile(
    aes(
      x = lon,
      y = lat,
      fill = mean,
      col = mean
    )
  ) +
  geom_sf(data = land_sf, aes()) +
  facet_wrap(~ state  +  region,
             ncol = 4) +
  labs(x = "Longitude", y = "Latitude") +
  scale_fill_viridis("Mean Interpolation", alpha = 0.8) +
  scale_color_viridis("Mean Interpolation", alpha = 0.8) +
  theme_bw()
```

@@

### Paper figure; Per species maps

@@

# The plot
map_plot <- land_sf %>% 
  left_join(state_fit,
            by = "state") %>% 
  ggplot() +
  geom_sf(aes(fill = mean_per)) +
  viridis::scale_fill_viridis("Average proportion per State", alpha = 0.8) +
  facet_grid(spp ~ label) +
  labs(x = "Longitude", 
       y = "Latitude") +
  my_ggtheme_p(facet_tx_s = 20,
               leg_pos = "bottom",
               axx_tx_ang = 45,
               ax_tx_s = 12,
               ax_tl_s = 18,
               hjust = 1) +
  theme(legend.key.width = unit(4,"line"))

  ggsave(filename = "proportion_chg_spp.jpg",
         plot = map_plot,
         path = my_path("R","Figures"),
         width = 14,
         height = 14
         )

@@

![Proportion change per species map for paper](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/proportion_chg_spp.jpg)
